Blog post: Identifying and manipulating non-breaking spaces

### 2020-02-29 text/20/non-breaking-space.Rmd
Added a bunch of spreadsheet recommendations.

![![Figure 1. Screenshot of a file inside Notepad](non-breaking-space01.png not found.](../../../web/images/20/non-breaking-space.Rmd01.png)

@@

![![Figure 2. Screenshot of a file inside RStudio](non-breaking-space02.png not found.](../../../web/images/20/non-breaking-space.Rmd02.png)

>>>>

![Figure 1. Screenshot of a file inside Notepad](non-breaking-space01.png)

@@

![Figure 2. Screenshot of a file inside RStudio](non-breaking-space02.png)
